An Improved ANS Transaction Template

### 2018-01-26 paper.tex
some update about the flow

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at >$90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

Level   &           & Assay     &       & Machines  \\ 
        & Feed      & Product   & Feed  &           \\
\midrule
1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
5       & 0.8834    & 0.9735    & 0.7746 & 169       \\

@@

\section{Results}

\subsection{wWithout tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.
Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
produce a an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.
This is the consequence of the usage of un-touched cascade in the case 1:
because the cut value at each stage is unchanged it artificially produces over
enricht tails when feeded with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.
The effective cut values for each cascade can be computed as :
\begin{equation}\label{eq:theta_eff}
    \theta = \dfrac{N - N''}{N'-N''}
\end{equation}

@@

    Looks at the effective $\theta$ values of the cascade at the third level in both
case

\subsection{Assays}
\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.

>>>>

All cases will be considered with and without tail recycling. Figure
\ref{fig:flow} shows the different flows between the different facilities in the
fleet, in a configuration with two different levels of cascade without tail
recycling. When considering the tail recycling, all the flow going from a
cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src correspond to an
      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
      corresponds respectively to the cascades, and the storage getting the
  products of the cascades at the level $n$.}\label{fig:flow}
\end{figure}

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

Level   &           & Assay     &       & Machines  \\ 
        & Feed      & Product   & Feed  &           \\
\midrule
0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
4       & 0.8834    & 0.9735    & 0.7746 & 169       \\

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{} and \ref{}, the first case is able to produce a an uranium product enrich
at $98\%$ while the second case is only able to reach an enrichment of $88.3\%$.

Because the cut value at each stage is unchanged it artificially produces over
enriched tails when feed with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.  The effective
cut values for each cascade can be computed as :

\begin{equation}\label{eq:theta_eff}
    \theta = \dfrac{N - N''}{N'-N''}
\end{equation}

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ as a function of the cascade level and the
  case considered.}
  \label{tab:cascade_theta}
\end{table}
As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
different level increase up to $0.54$ for the fifth stage on case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

\subsubsection{tails recycling}

\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.
